\documentclass[a4paper]{article}

\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{float}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algorithmic}
%\renewcommand{\algorithmicrequire}{\textbf{Initialization:}}
%\renewcommand{\algorithmicensure}{\textbf{Inference:}}

\geometry{left=3cm,right=3cm,top=3.75cm,bottom=3.75cm}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}


\begin{document}

\newtheorem{thm}{Theorem}
\newtheorem*{thm*}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{cla}{Claim}
\newtheorem{prop}{Proposition}

\title{Milestone 2 Report}

\author{Lei Zhong, Hantian Zhang, Jian Zhang}
\date{}
\maketitle

\abstract{Climate change has been one of the major global concerns regarding the ecosystem. By effectively analysing the pattern of climate change, we would be able to revolutionize our strategy in preserving ecosystems and sustainable development. Nowadays, millions of sensors have been
deployed to monitor different climate measurement, which generate gigantic volume of data in every minute. The amount of data exerts challenges for efficient analysing after accumulation over several decades. One of most challenging parts lies in the visualization of climate type and evolving pattern, which would be an essential step to turn noisy and large-scale data into source of meaningful information. In milestone 2, we use data collected in 2013 as a toy example to illustrate our algorithm on clustering visualizing climate pattern. We employ unsupervised clustering approach to classify different climate types and visualize our clustering results with GoogleMap. In our experiment, we observe reasonable clustering of climate patterns with respect to geological property and development level. In the future, we will utilize much larger volume of data (spanning over 90 years) and extend to visualizing the evolution of climate patterns.}

\input{data}
\input{design}
\input{result}

%\bibliographystyle{plain}
%\bibliography{Proposal}

\end{document}
