\documentclass[a4paper]{article}

\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{verbatim}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{float}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algorithmic}
%\renewcommand{\algorithmicrequire}{\textbf{Initialization:}}
%\renewcommand{\algorithmicensure}{\textbf{Inference:}}

\geometry{left=3cm,right=3cm,top=3.75cm,bottom=3.75cm}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}


\begin{document}

\newtheorem{thm}{Theorem}
\newtheorem*{thm*}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{cla}{Claim}
\newtheorem{prop}{Proposition}

\title{CLUE: A System to Cluster and Visualize the Global Historical Climatology Network}

\author{Lei Zhong, Hantian Zhang, Jian Zhang}
\date{}
\maketitle

\abstract{Climate change has been one of the major global concerns regarding the ecosystem. By effectively analysing the pattern of climate change, we would be able to revolutionize our strategy in preserving ecosystems and sustainable development. Millions of sensor has been deployed to monitor different climate measurement, which generate gigantic volume of data in every minute. The amount of data exerts challenges for efficient analysing after accumulation over
several decades. One of most challenge lies in the visualization of climate type and evolving pattern, which would be an essential step to turn noisy and large-scale data into source of meaningful information. In addition to the previous work we have done, We did more experiment with different parameters during the Milestone 4. We optimized the code and visualized the results as a video on youtube\cite{youtube}. In this final report, we will summarize over the whole three-month
project, demonstrate the results and point out some future work. }


\input{introduction}
\input{contribution}
\input{architecture}
\input{results}
\input{conclusion}

%\bibliographystyle{plain}
%\bibliography{Proposal}
\begin{thebibliography}{1}
    \bibitem{EMR} http://aws.amazon.com/elasticmapreduce/
    \bibitem{GHCN-D} Peterson, Thomas C., and Russell S. Vose. ``An overview of the Global Historical Climatology Network temperature database.'' Bulletin of the American Meteorological Society 78.12 (1997): 2837-2849.
    \bibitem{boto} https://boto.readthedocs.org/en/latest/
    \bibitem{S3} http://aws.amazon.com/de/s3/
    \bibitem{sklearn} http://scikit-learn.org/stable/
    \bibitem{GoogleMap} https://developers.google.com/maps/?hl=de
    \bibitem{youtube} https://www.youtube.com/watch?v=xQfEk978IE4\&list=UUkzQg0KkXhibidSnmizd4Vg\&index=2
    \bibitem{climatechallenge} http://unglobalpulse.org/big-data-climate/
    \bibitem{nasa} http://www.nas.nasa.gov/SC14/demos/demo33.html
    \bibitem{world} http://www.ngdc.noaa.gov/mgg/image/color\_etopo1\_ice\_low.jpg
\end{thebibliography}

\end{document}

